\bf On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2024-11-14 Manuscript/manuscript.tex
Added most current results to table 1

\begin{table}
  \centering
  \caption{2019 vs 2022 compares data from the same athletes who competed at the
  2019 and 2022 World Track and Field Championships. 2022 vs 2023 compares data
  from the same athletes who competed at the 2022 and 2023 World Track and Field
  Championships. National vs International compares data from the same athletes
  who competed at 2022 national-level championships and the 2022 World Track and
  Field Championships.}
  \begin{tabular}{c c c c c} 
   \toprule
   Comparison & Permutation & Asymptotic \\ 
   \midrule
   2019 vs 2022 & $0.028$ & $0.003$ \\
   2022 vs 2023 & $0.011$ & $0.003$ \\
   2022 National vs International & $<0.001$ & $0.002$ \\
   \bottomrule
  \end{tabular}
  \label{tab:Clusrankresults}
\end{table}

@@

\begin{table}
  \centering
  \caption{AIC and estimated parameters for the three models fitted to the
    data.}
  \label{tab:Gamma_parameters}
  \begin{tabular}{c c c c c c c}
    \toprule
    Data set & Model & AIC & $\sigma_h$ & $\sigma_v$ & $\alpha$ & $\sqrt{\phi}$ \\
    \midrule
    Excluding 2022 &
      Venue Effect Only & $-1862.2$ &   & 0.048 & $-1.857$ & 0.152\\
     & Heat Effect Only & $-1910.9$ & 0.069 &  & $-1.877$ & 0.136\\
     & Venue and Heat Effect & $-1912.9$ & 0.058 & 0.033 & $-1.868$ & 0.136\\[1ex]
    Including 2022 &
    Venue Effect Only & $-3798.8$ &   & 0.054 & $-1.871$ & 0.149\\
    & Heat Effect Only & $-2070.7$ & 0.073 &  & $-1.890$ & 0.135\\
    & Venue and Heat Effect & $-2075.7$ & 0.057 & 0.040 & $-1.881$ & 0.134\\
    \bottomrule
  \end{tabular}
\end{table}
\of{needs to be updated}

>>>>

\begin{table}
  \centering
  \caption{2019 vs 2022 compares data from the same athletes who competed at the
  2019 and 2022 World Track and Field Championships. 2022 vs 2023 compares data
  from the same athletes who competed at the 2022 and 2023 World Track and Field
  Championships. National vs International compares data from the same athletes
  who competed at 2022 national-level championships and the 2022 World Track and
  Field Championships.}
  \begin{tabular}{c c c c c} 
   \toprule
   Comparison & Permutation & Asymptotic & Athletes & Number observations  \\ 
   \midrule
   2019 vs 2022 Men & $2.8 \cdot 10^{-5}$ & $1.1 \cdot 10^{-5}$ & 34 & 134 \\
   2019 vs 2022 Female & $ 1.5 \cdot 10^{-3}$ & $6.9 \cdot 10^{-3}$ & 31 & 124 \\
   2022 National vs International Men & $<0.001$ & $ 6.1 \cdot 10^{-5}$ & 17 & 80 \\
   2022 National vs International Women & $<0.001$ & $ 1.2 \cdot 10^{-3}$ & 17 & 80 \\
   2022 vs 2023 Men & $<0.001$ & $1.4 \cdot 10^{-6}$ & 45 & 161 \\
   2022 vs 2023 Female & $<0.001$ & $9.4 \cdot 10^{-7}$ & 47 & 182 \\
   \bottomrule
  \end{tabular}
  \label{tab:Clusrankresults}
\end{table}
\of{Table currently doesnt fit on the page but can be fixed by abbreviating some
of the names in the comparison column.  I used <0.001 becuase that is what we
had currently been using for any values from the permutation test where the value
was < 2.2e-16 in R.  Professor Yan will know best, but are the sample sizes now
sufficiently large enough that the permutation test is not needed? If I recall
correctlty that was a correction for small sample sizes.}

@@

\begin{table}
  \centering
  \caption{AIC and estimated parameters for the three models fitted to the
    data.}
  \label{tab:Gamma_parameters}
  \begin{tabular}{c c c c c c c}
    \toprule
    Data set & Model & AIC & $\sigma_h$ & $\sigma_v$ & $\alpha$ & $\sqrt{\phi}$ \\
    \midrule
    Excluding 2022 &
      Venue Effect Only & $-1862.2$ &   & 0.048 & $-1.857$ & 0.152\\
     & Heat Effect Only & $-1910.9$ & 0.069 &  & $-1.877$ & 0.136\\
     & Venue and Heat Effect & $-1912.9$ & 0.058 & 0.033 & $-1.868$ & 0.136\\[1ex]
    Including 2022 &
    Venue Effect Only & $-3798.8$ &   & 0.054 & $-1.871$ & 0.149\\
    & Heat Effect Only & $-2070.7$ & 0.073 &  & $-1.890$ & 0.135\\
    & Venue and Heat Effect & $-2075.7$ & 0.057 & 0.040 & $-1.881$ & 0.134\\
    \bottomrule
  \end{tabular}
\end{table}
\of{needs to be updated with current values. But I did start to alter something
then stopped.}
